### 2013-12-12 manuscripts/reply/short-reply.tex
Incorporting Jake's edits of reply ms.

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Biogeographers frequently seek to explain population and species
    differentiation on geographical phenomena.
    Establishing that a set of population splitting events occurred
    at the same time can be a potentially persuasive argument that a set of taxa
    were affected by the same geographic events.
    Unfortunately, estimating divergence times precisely when one lacks
    precise information about the rate of molecular evolution is a notoriously
    difficult problem in evolutionary biology.
    \citep{Huang2011} introduced an approximate Bayesian approach which can be
    used to estimate the probabilities of models in which multiple sets of taxa
    diverge at the same time. 
    This method (implemented in the software \msb) does not require a common
    set of character data that links all of the taxa under investigation, but
    does require the relative mutation rates among the taxa and loci to be
    assumed \emph{a priori}.
    Recently, \citet{Oaks2012} used this model-choice framework to 
    study 22 pairs of vertebrate lineages which are distributed across
    the Philippines; they also studied the behavior of the \msb approach
    using computer simulations.
    \citet{Oaks2012} found that the model was very sensitive to the 
    prior that is chosen and that the inference method had low power
    to detect variation in divergences times.
    These results were not surprising, in light of a rich statistical literature
    that shows that the marginal likelihood of a model is quite sensitive to the
    use of vague priors.
    Because this sensitivity to prior assumptions affects the crucial insights 
    that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
    that users of the approach should carefully assess the robustness of their 
    conclusions to different priors.
    According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
    was due to excessively broad priors on divergence times leading to 
    inadequate numbers of simulation replicates.
    They proposed a new model-averaging approach that uses narrow, empirically informed uniform
    priors.
    Here we demonstrate that the approach of \citet{Hickerson2013} is
    dangerous in the sense that the empirically-derived priors often
    exclude from consideration the true values of the models' parameters.
    On a more fundamental level, we question the value of adopting an 
    empirical Bayesian stance for this model-choice problem.
    The robust Bayesian approach of conducting analyses under a variety
    of priors can reveal prior sensitivity and communicate which assumptions
    underlie model inference.
    Furthermore, simulations provide insight into the temporal resolution of
    the method, which in turn helps guide interpretation of results.

@@

\newpage
\msb
\citep{Huang2011} uses approximate Bayesian computation (ABC) to
estimate the distribution of divergence times among co-distributed pairs of
taxa.
It approximates a posterior probability over models that range from a single
divergence-time parameter (i.e., simultaneous divergence of all pairs of taxa)
to the fully generalized model in which each pair of taxa diverged at a
unique time.
A full description of the model is given in \citet{Oaks2012}.
Frequently, the exact values of the divergence times are hard 
to determine because researchers typically lack precise knowledge 
of the rate at which substitutions occur.
So the exact divergence time is often viewed as a nuisance parameter, and
researchers focus on the number of divergence events.
The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
on the fundamental methodological point about the model selection performed in \msb:
\begin{itemize}
   \item The use of vague priors on the divergence-time parameters can lead to
       support models with few divergence events shared across taxa. Thus, the
       primary inference enabled by the approach is very sensitive to the
       priors on divergence times.
\end{itemize}

This is not surprising given the rich statistical literature that shows that
model marginal likelihoods are quite sensitive to the priors used in Bayesian
model selection
\citep[e.g.,][]{Jeffreys1935,Lindley1957}.
Accordingly, \citet{Oaks2012} suggest the primary cause of the spurious support
for models with few divergence parameters is the greater marginal likelihoods
of these models under vague uniform priors, relative to more parameter-rich
models.
Models with more divergence-time parameters integrate over \emph{much} greater
parameter space with low probability of producing the data, yet relatively high
prior density imposed by the uniformly distributed prior on divergence times.
Note, this is a statistical issue, extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.

\citet{Hickerson2013} suggest the bias is the result of a numerical issue
intrinsic to \msb, concluding the method's rejection algorithm is inefficient
and will be biased toward models with fewer divergence-time parameters, because
the parameter space of these models are more densely sampled relative to models
with more divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results of additional analyses that, when combined with the results
of \citet{Oaks2012}, strongly suggest that \msb prefers models with few
divergence-time parameters, because they have greater likelihoods when
averaged over broad uniform priors on divergences times.

@@

\citet{Hickerson2013} suggest that \citet{Oaks2012} should have used their
data to inform their prior on divergence times (i.e., an empirical Bayesian
approach).
However, \citet{Oaks2012} did use empirically informed priors to mimic
empirical situations in which a large amount of prior information is available;
they did so to assess the prior sensitivity of the method and to determine if
uniform priors in such situations are narrow enough to avoid spurious support
of models with few divergence-time parameters.
The results of \citet{Oaks2012} and \citet{Hickerson2013} show the method is
highly sensitive to the prior on divergence times.
Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
divergences under the informed priors.

@@

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the fairness of a particular coin, and we
denote the unknown probability of it landing heads as \myTheta{}.
More specifically, we are interested in the probability of two models, $M_1$
and $M_2$.
In both models the outcomes of flipping the coin are assumed to be binomially
distributed, but under $M_1$ the coin is weighted toward landing heads (i.e.,
$\myTheta{} > 0.5)$), whereas under $M_2$, the coin is weighted toward landing
tails (i.e., $\myTheta{} < 0.5$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times, and so we decide to use these data in specifying a
beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin of interest $N=10$ times, $y=3$ of which
land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$
(Figure~\ref{figCoinFlip}).
The maximum a posteriori (MAP) estimate of the probability of heads is 0.429,
and following Equation~\ref{eq:marginallikelhiood} the marginal likelihoods of
our models of interest are
\begin{equation}
    p(y=3, N=10 \given M_1) = \int_{0.5}^{1} p(y=3, N=10 \given
    \myTheta{}, M_1)p(\myTheta{} \given M_1) d\myTheta{} \approx 0.029,
\end{equation}
and
\begin{equation}
    p(y=3, N=10 \given M_2) = \int_{0}^{0.5} p(y=3, N=10 \given
    \myTheta{}, M_2)p(\myTheta{} \given M_2) d\myTheta{} \approx 0.097.
\end{equation}
Given the models have equal probability under our prior, we can calculate the
posterior probability of Model 1 as
\begin{equation}
    p(M_1 \given y=3, N=10) = \frac{p(y=3, N=10 \given M_1)}{p(y=3, N=10 \given
    M_1) + p(y=3, N=10 \given M_2)} \approx 0.23.
\end{equation}
This is the correct posterior probability of Model 1 given our prior
and data.

@@

The strong preference for the questionable priors on divergence times (their
$M_1$ and $M_2$) in the model-averaged results of \citet{Hickerson2013} suggest
their approach is biased toward models with less parameter space, and as a
consequence, is biased toward estimating model-averaged posteriors dominated by
models that exclude true values of parameters of the model.
We explored this possibility in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

Given the theoretical and practical issues with empirical Bayes approaches to
Bayesian model choice, it is clear why one should use caution before overly
criticizing an investigator's choice of priors after having seen the resulting
posterior.
%In a strictly Bayesian world, this is cheating.
As discussed by \citet{Oaks2012}, prior to analyzing the data, there was a
large amount of uncertainty regarding the divergence times of the 22 population
pairs under study.
Two of these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
Siler2011,Siler2012,RafeStuart2012,LinkemBrown2013,Rafe2013AREES,Siler2014kikuchii}.
% \citet{Oaks2012} also discuss how uniform priors on postive real-valued parameters make
% it difficult for investigators to express their prior uncertainty without
% putting high prior density in regions of improbable parameter space.
When limited to uniformly distributed priors, the alternative to priors that
reflect prior uncertainty, as shown above, is to risk excluding the true values
one seeks to estimate.
However continuous distributions perhaps more appropriate as priors for
positive real-valued parameters have been shown to greatly reduce spurious
support for clustered divergence models while allowing prior uncertainty to be
accommodated \citep{Oaks2014dpp}.

@@

Also, the results of our power analyses further demonstrate the propensity of
Hickerson et al.'s (\citeyear{Hickerson2013}) approach to exclude true
parameter values.
Across all but one of the \divt{max} we simulated, in a large proportion of
replicates the method favors a model that excludes the truth, and across many
of the \divt{max} the preferred model will exclude a large proportion of the
true divergence-time values (Figure~\ref{figPowerNumExcluded}).
Importantly, the posterior probability of excluding at least on true divergence
value is also quite high across many of the \divt{max}
(Figure~\ref{figPowerProbExclusion}).
Only when the data are identically distributed as one of the prior models does
the method avoid excluding the truth more than 5\% of the time
(Figure~\ref{figPowerNumExcluded}E).
Again, this demonstrates the method's sensitivity to priors.

@@

As noted by \citet{Oaks2012}, inferring more than one divergence time
shared across all taxa does not confirm the method is working well when
analyzing data generated under random temporal variation in divergences (e.g.,
an inference of two divergence events could be biogeographically interesting
yet spurious).
Thus, it is important that investigators not limit their assessment of method's
power to only differentiating inferences of one event or more (i.e. $\numt{} =
1$ versus $\numt{} > 1$).
Rather, looking at the distribution of estimates, as in \citet{Oaks2012},
provides much more information about the behavior of the method.

@@

To disentangle whether model likelihoods or insufficient prior sampling is to
blame for the method's spurious support for simple models, we must look at the
different predictions made by these two phenomena.
One example, as discussed by \citet{Oaks2012}, is that insufficient prior
sampling should create large variance among posterior estimates, and thus it
should cause analyses to be highly sensitive to the number of samples drawn
from the prior.
Furthermore, if sampling error is biased toward models with less
parameter space, as suggested by \citet{Hickerson2013}, we expect to see
support for these models decrease as sampling increases.
\citet{Oaks2012} do not see such sensitivity when they compare prior sample
sizes of $2\e6$, $5\e6$, and $10^7$.

@@

\section*{General thoughts on the model of \msb}
Our findings are not very surprising in light of difficult inference problem
\msb seeks to tackle.
To get a sense of the challenge \msb is faced with, we tally up all the free
parameters of the \msb model as applied to the dataset of \citet{Oaks2012}.
% While this approach is trivial to implement, it is not a trivial change
% to the \msb model.
% To better understand the reason for this, it might help to step back and get a
% sense of the scale of the \msb model.
% To do this, we will use the dataset of 22 vertebrate taxon pairs of
% \citet{Oaks2012} as an example.
% Following the model description and notation of \citet{Oaks2012}, let us tally
% up all of the free parameters in the \msb model.
Under the simplest model in \msb (i.e., assuming no migration and no
intra-locus recombination), the number of parameters for each taxon pair
include:
The population sizes of the ancestral and descendant populations
(\ancestralTheta{}, \descendantTheta{1}{}, \descendantTheta{2}{}),
the magnitude of population contraction in each of the descendant
populations (\bottleScalar{1}{} and \bottleScalar{2}{}) and the
timing of these contractions (\bottleTime{}), and the $N-1$ node heights
(coalescent times) of the gene tree that gave rise to the $N$ gene
copies sampled from both populations of the pair.
% Because we only have a single locus for each taxon, there are no locus-specific
% \myTheta{}-scaling parameters (\locusMutationRateScalar{}) or
% \locusRateHetShapeParameter shape parameter for the gamma prior distribution on
% \locusMutationRateScalar{}.
Lastly, there are between one and 22 divergence time parameters \divt{} in
the vector \divtvector.
Overall, when applying the simplest model in \msb to the dataset of
\citet{Oaks2012} with 22 taxon pairs, there are 581--602 free parameters
(depending on the number of divergence-time parameters in \divtvector).
Furthermore, under this rich model, the method is estimating the probability of
1002 divergence models \citep[i.e., the number of integer partitions of
$Y=22$;][]{Oaks2012}.

>>>>

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Biogeographers frequently seek to explain population and species
    differentiation on geographical phenomena.
    Establishing that a set of population splitting events occurred
    at the same time can be a potentially persuasive argument that a set of taxa
    were affected by the same geographic events.
    Unfortunately, estimating divergence times precisely when one lacks
    precise information about the rate of molecular evolution is a notoriously
    difficult problem in evolutionary biology.
    \citep{Huang2011} introduced an approximate Bayesian approach which can be
    used to estimate the probabilities of models in which multiple sets of taxa
    diverge at the same time. 
    This method (implemented in the software \msb) does not require a common
    set of character data that links all of the taxa under investigation, but
    does require the relative mutation rates among the taxa and loci to be
    assumed \emph{a priori}.
    Recently, \citet{Oaks2012} used this model-choice framework to 
    study 22 pairs of vertebrate lineages which are distributed across
    the Philippines; they also studied the behavior of the \msb approach
    using computer simulations.
    \citet{Oaks2012} found that the model was very sensitive to the prior and
    that the inference method had low power to detect variation in divergences
    times.
    These results were not surprising, in light of a rich statistical literature
    showing that the marginal likelihood of a model is sensitive to the
    use of vague priors.
    Because this sensitivity to prior assumptions affects the crucial insights 
    that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
    that users of the approach should carefully assess the robustness of their 
    conclusions to different priors.
    According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
    was due to excessively broad priors on divergence times, leading to 
    inadequate numbers of simulation replicates.
    They proposed a new model-averaging approach that uses narrow, empirically
    informed uniform priors.
    Here we demonstrate that the approach of \citet{Hickerson2013} is
    dangerous in the sense that the empirically-derived priors often
    exclude from consideration the true values of the models' parameters.
    On a more fundamental level, we question the value of adopting an empirical
    Bayesian stance for this model-choice problem, because it can mislead model
    posterior probabilities, which are inherently measures of belief in the
    models after prior knowledge is updated by the data.
    The robust Bayesian approach of conducting analyses under a variety
    of priors can reveal prior sensitivity and communicate which assumptions
    underlie model inference.
    Furthermore, simulations provide insight into the temporal resolution of
    the method, which in turn helps guide interpretation of results.

@@

\newpage
\msb
\citep{Huang2011} uses approximate Bayesian computation (ABC) to
estimate the distribution of divergence times among co-distributed pairs of
taxa.
It approximates a posterior probability over models that range from a single
divergence-time parameter (i.e., simultaneous divergence of all pairs of taxa)
to the fully generalized model in which each pair of taxa diverged at a
unique time.
A full description of the model is given in \citet{Oaks2012}.
Frequently, the exact values of the divergence times are hard 
to determine because researchers typically lack precise knowledge 
of the rate at which substitutions occur.
The exact divergence time is therefore often viewed as a nuisance parameter,
and researchers focus on the number of divergence events.
The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
on the fundamental methodological point about the model selection performed in \msb:
\begin{itemize}
   \item The use of vague priors on the divergence-time parameters can lead to
       support models with few divergence events shared across taxa. Thus, the
       primary inference enabled by the approach is very sensitive to the
       priors on divergence times.
\end{itemize}

This is not surprising given the rich statistical literature that shows that
model marginal likelihoods are quite sensitive to the priors used in Bayesian
model selection
\citep[e.g.,][]{Jeffreys1935,Lindley1957}.
Accordingly, \citet{Oaks2012} suggest the primary cause of spurious support
for models with few divergence parameters is the greater marginal likelihoods
of these models under vague uniform priors, relative to more parameter-rich
models.
Models with more divergence-time parameters integrate over \emph{much} greater
parameter space with low probability of producing the data, yet relatively high
prior density imposed by the uniformly distributed prior on divergence times.
Note, this is a statistical issue, extrinsic to \msb, and does not question the
soundness of the numerical approximation machinery of \msb.

\citet{Hickerson2013} suggest the bias is the result of a numerical issue
intrinsic to \msb, concluding the method's rejection algorithm is inefficient
and will be biased toward models with fewer divergence-time parameters, because
the parameter space of these models are more densely sampled relative to models
with more divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results here of analyses that, when combined with the results
of \citet{Oaks2012}, strongly suggest that \msb prefers models with few
divergence-time parameters, because they have greater likelihoods when
averaged over broad uniform priors on divergences times.

@@

\citet{Hickerson2013} suggest that \citet{Oaks2012} should have used their
data to inform their prior on divergence times (i.e., an empirical Bayesian
approach).
However, \citet{Oaks2012} did use empirically informed priors to mimic
empirical situations in which a large amount of prior information is available;
they did so to assess the prior sensitivity of the method and to determine if
uniform priors in such situations are narrow enough to avoid spurious support
of models with few divergence-time parameters.
The results of \citet{Oaks2012} and \citet{Hickerson2013} show the method is
highly sensitive to the prior on divergence times.
Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
divergences under the empirically informed priors.

@@

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the fairness of a particular coin, and we
denote the unknown probability of it landing heads as \myTheta{}.
More specifically, we are interested in the probability of two models, $M_1$
and $M_2$.
In both models the outcomes of flipping the coin are assumed to be binomially
distributed, but under $M_1$ the coin is weighted toward landing heads (i.e.,
$\myTheta{} > 0.5)$), whereas under $M_2$, the coin is weighted toward landing
tails (i.e., $\myTheta{} < 0.5$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times each, and so we decide to use these data in specifying
a beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin of interest $N=10$ times, $y=3$ of which
land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$
(Figure~\ref{figCoinFlip}).
The maximum a posteriori (MAP) estimate of the probability of heads is 0.429,
and following Equation~\ref{eq:marginallikelhiood} the marginal likelihoods of
our models of interest are
\begin{equation}
    p(y=3, N=10 \given M_1) = \int_{0.5}^{1} p(y=3, N=10 \given
    \myTheta{}, M_1)p(\myTheta{} \given M_1) d\myTheta{} \approx 0.029,
\end{equation}
and
\begin{equation}
    p(y=3, N=10 \given M_2) = \int_{0}^{0.5} p(y=3, N=10 \given
    \myTheta{}, M_2)p(\myTheta{} \given M_2) d\myTheta{} \approx 0.097.
\end{equation}
Given the models have equal probability under our prior, we can calculate the
posterior probability of Model 1 as
\begin{equation}
    p(M_1 \given y=3, N=10) = \frac{p(y=3, N=10 \given M_1)}{p(y=3, N=10 \given
    M_1) + p(y=3, N=10 \given M_2)} \approx 0.23.
\end{equation}
This is the correct posterior probability of Model 1 given our prior
and data.

@@

The strong preference for the questionable priors on divergence times (their
$M_1$ and $M_2$) in the model-averaged results of \citet{Hickerson2013} suggest
their approach is biased toward models with less parameter space, and as a
consequence, is biased toward estimating model-averaged posteriors dominated by
models that exclude true values of parameters of the model.
We explored this possibility in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging
approach of \citet{Hickerson2013}, but set one of the prior models with a
uniform prior on divergence times that is unrealistically narrow, and almost
certainly excludes most, if not all, of the true divergence times of the 22
taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

Given the theoretical and practical issues with empirical Bayes approaches to
Bayesian model choice, it is clear why one should use caution before overly
criticizing an investigator's choice of priors \emph{after} having seen the
resulting posterior.
%In a strictly Bayesian world, this is cheating.
As discussed by \citet{Oaks2012}, prior to analyzing the data, there was a
large amount of uncertainty regarding the divergence times of the 22 population
pairs under study.
Two of these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
Siler2011,Siler2012,RafeStuart2012,LinkemBrown2013,Rafe2013AREES,Siler2014kikuchii}.
% \citet{Oaks2012} also discuss how uniform priors on postive real-valued parameters make
% it difficult for investigators to express their prior uncertainty without
% putting high prior density in regions of improbable parameter space.
When limited to uniformly distributed priors, the alternative to priors that
reflect prior uncertainty, as shown above, is to risk excluding the true values
one seeks to estimate.
However continuous distributions perhaps more appropriate as priors for
positive real-valued parameters have been shown to greatly reduce spurious
support for clustered divergence models while allowing prior uncertainty to be
accommodated \citep{Oaks2014dpp}.

@@

Also, the results of our power analyses further demonstrate the propensity of
Hickerson et al.'s (\citeyear{Hickerson2013}) approach to exclude true
parameter values.
Across all but one of the \divt{max} we simulated, in a large proportion of
replicates the method favors a model that excludes the truth, and across many
of the \divt{max} the preferred model will exclude a large proportion of the
true divergence-time values (Figure~\ref{figPowerNumExcluded}).
Importantly, the posterior probability of excluding at least one true
divergence value is also quite high across many of the \divt{max}
(Figure~\ref{figPowerProbExclusion}).
Only when the data are identically distributed as one of the prior models does
the method avoid excluding the truth more than 5\% of the time
(Figure~\ref{figPowerNumExcluded}E).
Again, this demonstrates the method's sensitivity to priors.

@@

As noted by \citet{Oaks2012}, inferring more than one divergence time
shared across all taxa does not confirm the method is working well when
analyzing data generated under random temporal variation in divergences (e.g.,
an inference of two divergence events could be biogeographically interesting
yet spurious).
Thus, it is important that investigators not limit their assessment of the
method's power to only differentiating inferences of one event or more (i.e.
$\numt{} = 1$ versus $\numt{} > 1$).
Rather, looking at the distribution of estimates, as in \citet{Oaks2012},
provides much more information about the behavior of the method.

@@

To disentangle whether model likelihoods or insufficient prior sampling is to
blame for the method's spurious support for simple models, we must look at the
different predictions made by these two phenomena.
One example, as discussed by \citet{Oaks2012}, is that insufficient prior
sampling should create large variance among posterior estimates, and thus it
should cause analyses to be highly sensitive to the number of samples drawn
from the prior.
Furthermore, if sampling error is biased toward models with less
parameter space, as suggested by \citet{Hickerson2013}, we expect to see
support for these models decrease as sampling increases.
\citet{Oaks2012} did not see such sensitivity when they compared prior sample
sizes of $2\e6$, $5\e6$, and $10^7$.

@@

\section*{General thoughts on the model of \msb}
Our findings are not very surprising in light of difficult inference problem
\msb seeks to tackle.
To get a sense of the challenge \msb is faced with, we tally up all the free
parameters of the \msb model as applied to the dataset of \citet{Oaks2012}.
% While this approach is trivial to implement, it is not a trivial change
% to the \msb model.
% To better understand the reason for this, it might help to step back and get a
% sense of the scale of the \msb model.
% To do this, we will use the dataset of 22 vertebrate taxon pairs of
% \citet{Oaks2012} as an example.
% Following the model description and notation of \citet{Oaks2012}, let us tally
% up all of the free parameters in the \msb model.
Under the simplest model in \msb (i.e., assuming no migration and no
intra-locus recombination), the number of parameters for each taxon pair
include:
The population sizes of the ancestral and descendant populations
(\ancestralTheta{}, \descendantTheta{1}{}, \descendantTheta{2}{}),
the magnitude of population contraction in each of the descendant
populations (\bottleScalar{1}{} and \bottleScalar{2}{}), the
timing of these contractions (\bottleTime{}), and the $N-1$ node heights
(coalescent times) of the gene tree that gave rise to the $N$ gene
copies sampled from both populations.
% Because we only have a single locus for each taxon, there are no locus-specific
% \myTheta{}-scaling parameters (\locusMutationRateScalar{}) or
% \locusRateHetShapeParameter shape parameter for the gamma prior distribution on
% \locusMutationRateScalar{}.
Lastly, there are between one and 22 divergence time parameters \divt{} in
the vector \divtvector.
Overall, when applying the simplest model in \msb to the dataset of
\citet{Oaks2012} with 22 taxon pairs, there are 581--602 free parameters
(depending on the number of divergence-time parameters in \divtvector).
Furthermore, under this rich model, the method is estimating the probability of
1002 divergence models \citep[i.e., the number of integer partitions of
$Y=22$;][]{Oaks2012}.
